### 2014-05-13 tex/main-body-text.tex
added q-val plot & some results

\subsection*{Analysis of coastal California steelhead} 
To evaluate the preformance and computational efficiency of {\sc flock}  we used a published 
dataset from \citet{Garzaetal_norcal} comprised of 2596 steelhead \textit{Oncorhynchus mykiss}
genotyped at 15 microsatellite loci.  {\sc flock} was run six times using the default setting for all run parameters

\textit{(initial partition = random, number of iterations = 20, number of runs = 50, 
LLOD threshold = 0)} for values of \textit{k} from 2 to 6. The stopping point of 
\textit{k}=6 was chosen because four consecutive runs with 0 length plateaus were 
produced. The non-admixture, uncorrelated allele frequency model implemented in {\sc structure}
was run with six iterations of a 50,000 sweep burn-in followed by 150,000 sweep sample 
from the posterior of \textit{k} from 2 to 6. To facilitate the comparison of the two programs,
the program {\sc clump} \citep{Jak&Ros2007} was used to relabel clusters among different runs,
while the program Distruct \citep{Rosenberg2004} was used to plot individual \textit{$q_i$} values.

\subsection*{Results} 
Run times were relatively short. The four groups of runs for the default settings 
averaged 217 minutes (30min SD) on an i7 3.40GHz processor with 8GB of RAM. While no 
plateaus were observed in any of the four groups for a \textit{k} greater than two, 
the plateau record varied greatly among each group for \textit{k}=2 (plateau 
sequences- Run1=3,2,5,6,3; Run2=2,2,2,4,3,2; Run3=2,3,2,4; and Run4=2,3,3,4,2,2,5,2). 
The plateau analysis procedure suggested by \citet{Duc&Tur2012} leads to two different 
conclusions for the plateau sequences observed: \textit{k}=2 is the lower bound 
estimate (Run1) or there is no estimate (\textit{undecided}: Runs 2-4). Despite 
different conclusions, the allocation of individuals for the 'best run' from each 
group differed by a only a single individual. When \textit{k}=2, {\sc flock} 
identifies a boundary in the Russian Gulch area clustering individuals into northern 
and southern groups (Fig. 1).

@@

With increased \textit{k} {\sc flock} continues to splits individuals approximately 
based on geographical boundaries identified by \citet{Garzaetal_norcal} using {\sc 
structure}. Once \textit{k} = 6 is reached no new regions are identified.

>>>>

\subsection*{Analysis of coastal California steelhead} 
To evaluate the preformance and computational efficiency of {\sc flock}  we used a published 
dataset from \citet{Garzaetal_norcal} comprised of 2596 steelhead \textit{Oncorhynchus mykiss}
genotyped at 15 microsatellite loci.  {\sc flock} was run six times using the default setting for all run parameters \textit{(initial partition = random, number of iterations = 20, number of runs = 50, 
LLOD threshold = 0)} for values of \textit{k} from 2 to 6. The stopping point of 
\textit{k}=6 was chosen after four consecutive runs yielded no plateau. The non-admixture, uncorrelated allele frequency model implemented in {\sc structure} was run with six iterations of a 50,000 sweep burn-in followed by 150,000 sweep sample from the posterior of \textit{k} from 2 to 6. All runs were performed with an i7 3.40GHz processor and 8GB of RAM. To facilitate the comparison of the two programs,
the program {\sc clump} \citep{Jak&Ros2007} was used to relabel clusters among different runs,
while the program Distruct \citep{Rosenberg2004} was used to plot individual \textit{$q_i$} values.

\subsection*{Results} 
Run times were relatively short. The six groups of runs for the default settings 
averaged 188.8 minutes (1.5 min SD). While no  plateaus were observed in any of the six groups for a \textit{k} greater than two, the plateau record varied greatly among each group for \textit{k}=2 (plateau 
sequences- Run1= 3,2,3,5,2,4; Run2=2,5,2,3,2,3; Run3=2,2,2,2,2,5; Run4=2,3,4,2,2,2,3; Run5=2,2,2,4,3,2; 
and; Run6=2,3,3,4,2,2,5,2). The plateau analysis procedure suggested by \citet{Duc&Tur2012} leads to 
an \textit{undecided} estimate of K as a consequence of no plateau lengths being greater than 6. Despite 
the K estimation based on rules of thumb devloped by \citet{Duc&Tur2012}, Distruct plots for each group of runs 
for \textit{k}=2-4 lead to nearly identical clustering of individuals (See supplementary materials). While only two of the six 'best runs' when \textit{k}=2 ended with identical clustering (same mean LLOD score), all other runs differed by at most the allocation of 13 individuals. When \textit{k} was set to three and four all runs provided very similar clustering.

@@

With increased \textit{k} {\sc flock} continues to splits individuals approximately 
based on geographical boundaries identified by \citet{Garzaetal_norcal} using {\sc 
structure}.

\begin{figure*}
\begin{center}
    \includegraphics[width=\textwidth]{images/Figures-Pat/Qval-StrFloc.pdf}
    \caption{Individual \textit{$q_i$} values plotted for each cluster for \textit{k}=5. {\sc flock} estimates of likelihood of assignment to each cluster have less uncertainty attributed to them.}
    \label{Fig.2}
\end{center}
\end{figure*}
